Security Metrics for the Android Ecosystem

### 2015-07-23 spsm04-thomas.tex
Add footnote early on explaining what a critical vulnerability is

It has been previously shown that Android devices do not receive security updates promptly when critical vulnerabilities are publicly disclosed and hence, on average, \daMeanInsecurityPercNominal\ are exposed to known critical vulnerabilities~\cite{androidvulnerabilities.org}.
Here we attempt to determine why by understanding the Android update process, evaluating different entities in the ecosystem and producing a scoring metric to compare different entities.

>>>>

It has been previously shown that Android devices do not receive security updates promptly when critical vulnerabilities\footnote{If malicious code exploits a critical vulnerability then it gains control of the device.} are publicly disclosed and hence, on average, \daMeanInsecurityPercNominal\ are exposed to known critical vulnerabilities~\cite{androidvulnerabilities.org}.
Here we attempt to determine why by understanding the Android update process, evaluating different entities in the ecosystem and producing a scoring metric to compare different entities.
